---
# title: "reg_tables"
output: pdf_document
header-includes:
   - \usepackage{amsmath}
   - \usepackage{xcolor}
   - \usepackage{relsize}
# fontsize: 12pt
# linestretch: 1.5
---

```{r setup, include=FALSE}
library(stargazer)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      collapse = TRUE,
                      results = "hide",
                      comment = "#>")

# To ensure that the appropriate TeX packages are installed, run the following: 
# tinytex::check_installed('relsize')

# If FALSE, then run the following code:
# tinytex::tlmgr_search("relsize")
# tinytex::tlmgr_install("relsize")   # install the relsize package
# tinytex::tlmgr_update()             # update everything
```

```{r, include=FALSE}
# Importing R scripts
source("reg_models.R", local = knitr::knit_global())
source("data-exploration.R", local = knitr::knit_global())
```


```{r, results='asis'}
# Summary Statistics
stargazer(df.stats, 
          # type = "latex", 
          header = FALSE,    # gets ride of citation
          title = "Summary statistics for the subsetted data",
          digits = 0, 
          font.size = "small",
          covariate.labels = c("House price index (HPI)",
                               "Population",
                               'Unemployment rate*',
                               "Labour force participation rate*",
                               "Mortgage rate*",
                               
                               "Total housing completions",
                               "\\ \\ Completed single-detached units",
                               "\\ \\ Completed semi-detached units",
                               "\\ \\ Completed row units",
                               
                               "Total housing starts",
                               "\\ \\ Starts on single-detached units",
                               "\\ \\ Starts on semi-detached units",
                               "\\ \\ Starts on row units",
                               
                               "Total under construction (u.c.)",
                               "\\ \\ Single-detached units (u.c.)",
                               "\\ \\ Semi-detached units (u.c.)",
                               "\\ \\ Row units (u.c.)",
                               
                               "Median income",
                               "Income of couples with kids",
                               "Population aged under 17",
                               "Population aged 18-64",
                               "Population aged 65 and over",
                               "Total number of Families",
                               "Total families with children",
                               escape = FALSE),
          notes.align = "l",
          notes = c("*variables with an asterisk(*) are percentage figures"),
          omit.summary.stat = c("sd"),
          notes.append = TRUE)
```

_Note_: The table above describes the summary statistics of the final compiled and subsetted dataset for 24 variables.

\newpage

```{r, results='asis'}
# Changing the format of the column names
sum_HPI$GEO <- c("Calgary", 
                 "Edmonton", 
                 "Guelph$\\color{red}^\\mathlarger{*}$", 
                 "Hamilton$\\color{red}^\\mathlarger{*}$", 
                 "Kelowna$\\color{blue}^\\ddagger$", 
                 "Kitchener$\\color{red}^\\mathlarger{*}$", 
                 "London$\\color{red}^\\mathlarger{*}$",
                 "Montreal", 
                 "Niagara$\\color{red}^\\mathlarger{*}$", 
                 "Oshawa$\\color{red}^\\mathlarger{*}$",
                 "Ottawa", 
                 "Sudbury", 
                 "Toronto$\\color{red}^\\mathlarger{*}$", 
                 "Vancouver$\\color{blue}^{\\dagger \\ddagger}$", 
                 "Victoria$\\color{blue}^\\ddagger$", 
                 "Windsor")

# Summary statistics for the HPI
kbl(sum_HPI, 
    caption = "Summary statistics for House Price Index (HPI) across all 16 cities in the data",
    booktabs = T,
    format = "latex",
    digits = c(0, 0, 2, 2, 1, 2, 2, 2, 1),
    col.names = c("City", "N", "Mean", "St. Dev.", "Min", "Q1", "Median", "Q3", "Max"),
    linesep = "",
    escape = FALSE
    ) %>% kable_styling(latex_options = c("striped", "hold_position"))

```

_Note_: Summary statistics for those regions marked with the red asterisk(\*) are where the NRST applied, and the cities marked with the blue dagger($\dagger$) and double-dagger($\ddagger$) represent the cities for which different versions of the APTT applied to (i.e., $\dagger$APT1, $\ddagger$APT2).


\newpage

```{r, results='asis'}
# Base DID Model
stargazer(did.base, 
          type = "latex",
          header = FALSE,    # gets ride of citation
          dep.var.labels = c("log(HPI)"),
          font.size = "normalsize",
          # out = "~\\Projects\\spec-tax-project\\Analysis\\did_base_reg.html",
          title = "Base difference-in-differences (DID) regression model",
          order = c("Constant",
                    "tr_NRST:NRST", 
                    "tr_APT1:APT1", 
                    "tr_APT2:APT2",
                    
                    "tr_NRST",
                    "NRST",
                    "tr_APT1",
                    "APT1",
                    "tr_APT2",
                    "APT2"
                    ),
          covariate.labels = c("Constant",
                               "NRST interaction",
                               "ABT1 interaction",
                               "ABT2 interaction",
                               
                               "NRST regional dummy",
                               "NRST post-treatment dummy",
                               "ABT1 regional dummy",
                               "ABT1 post-treatment dummy",
                               "ABT2 regional dummy",
                               "ABT2 post-treatment dummy"
                               ),
          # notes = c("all variables are log transformations"),
          notes.append = FALSE,
          column.separate = c(1, 1)
          # omit.stat = c("f", "ser","rsq")
          )
```

_Note_: The table above shows the results of the simple difference-in-differences base model. The dependent variable is the logarithmic transformation of the New Housing Price Index.

\newpage

```{r, results='asis'}
# Full DID Model w/ all model specs, removed: did.hc
stargazer(did.base, did.ctrls, did.ctrls2, did.hc2, did.demo, did.inc, did.all, did.all2,
          title = "DID regression models with controls and log(HPI) as the dependent variable",
          header = FALSE,    # gets ride of citation
          type = "latex",
          # out = "~\\Projects\\spec-tax-project\\Analysis\\did_full_reg.html",
          dep.var.labels.include = FALSE, 
          font.size = "footnotesize",
          column.sep.width = "-10pt",
          style = "aer",
          keep=c("Constant", 
                 "tr_NRST:NRST", 
                 "tr_APT1:APT1", 
                 "tr_APT2:APT2",
                 "lnPop", 
                 "lnFam", 
                 "lnUR", 
                 "lnLFPR", 
                 "lnMort", 
                 "lnInc_med", 
                 "lnInc_Cwkids",
                 "lnStarts_total", 
                 "lnStarts_single", 
                 "lnStarts_semi", 
                 "lnStarts_row", 
                 "lnCompl_total", 
                 "lnCompl_single", 
                 "lnCompl_semi", 
                 "lnCompl_row"),
          # omit = c("tr_NRST", "NRST", "tr_APT1", "APT1", "tr_APT2", "APT2"),
          order = c("Constant", 
                    "tr_NRST:NRST", 
                    "tr_APT1:APT1", 
                    "tr_APT2:APT2",
                    
                    # "tr_NRST", 
                    # "NRST", 
                    # "tr_APT1", 
                    # "APT1", 
                    # "tr_APT2", 
                    # "APT2", 
                    
                    "lnPop", 
                    "lnFam", 
                    "lnUR", 
                    "lnLFPR", 
                    "lnMort", 
                    "lnInc_med", 
                    "lnInc_Cwkids",
                    
                    "lnStarts_total", 
                    "lnStarts_single", 
                    "lnStarts_semi", 
                    "lnStarts_row", 
                    
                    "lnCompl_total", 
                    "lnCompl_single", 
                    "lnCompl_semi", 
                    "lnCompl_row"
                    ),
          covariate.labels = c("Constant",
                               "NRST interaction",
                               "ABT1 interaction",
                               "ABT2 interaction",
                               
                               # "NRST regional dummy",
                               # "NRST post-treatment dummy",
                               # "ABT1 regional dummy",
                               # "ABT1 post-treatment dummy",
                               # "ABT2 regional dummy",
                               # "ABT2 post-treatment dummy",
                               
                               "Population",
                               "Number of Families",
                               "Unemployment rate",
                               "Labour force participation rate",
                               "Mortgage rate",
                               "Median income",
                               "Income of couples with kids",
                               
                               "Total construction starts",
                               "\\ \\ \\ \\ \\ Starts on single-detached units",
                               "\\ \\ \\ \\ \\ Starts on semi-detached units",
                               "\\ \\ \\ \\ \\ Starts on row units",
                               "Total construction completions",
                               "\\ \\ \\ \\ \\ Completed single-detached units",
                               "\\ \\ \\ \\ \\ Completed semi-detached units",
                               "\\ \\ \\ \\ \\ Completed row units",
                               escape = FALSE
                               ),
          # omit = c("NRST regional dummy", "NRST post-treatment dummy", "ABT1 regional dummy",
          #                      "ABT1 post-treatment dummy", "ABT2 regional dummy",
          #                      "ABT2 post-treatment dummy"),
          notes = c("all variables are log transformations,          ∗ p<0.1; ∗∗ p<0.05; ∗∗∗ p<0.01"),
          notes.append = FALSE,
          column.separate = c(1, 1),
          omit.stat = c("f", "ser","rsq"))
```

_Note_: The table above shows the results of the full difference-in-differences base model with controls.

\newpage

```{r, results='asis'}
# Full FE DID Model
stargazer(fe.base, fe.ctrls, fe.ctrls2, fe.hc2, fe.demo, fe.inc, fe.all, fe.all2,
          title = "Fixed effects difference-in-differences regression models with log(HPI) as the dependent variable",
          header = FALSE,    # gets ride of citation
          type = "latex",
          # out = "~\\Projects\\spec-tax-project\\Analysis\\fe_reg.html",
          dep.var.labels.include = FALSE, 
          font.size = "footnotesize",
          column.sep.width = "-10pt",
          style = "aer",
          keep=c("tr_NRST:NRST", 
                 "tr_APT1:APT1", 
                 "tr_APT2:APT2",
                 "lnPop", 
                 "lnFam", 
                 "lnUR", 
                 "lnLFPR", 
                 "lnMort", 
                 "lnInc_med", 
                 "lnInc_Cwkids",
                 "lnStarts_total", 
                 "lnStarts_single", 
                 "lnStarts_semi", 
                 "lnStarts_row", 
                 "lnCompl_total", 
                 "lnCompl_single", 
                 "lnCompl_semi", 
                 "lnCompl_row"),
          # omit = c("tr_NRST", "NRST", "tr_APT1", "APT1", "tr_APT2", "APT2"),
          order = c("tr_NRST:NRST", 
                    "tr_APT1:APT1", 
                    "tr_APT2:APT2",
                    
                    # "tr_NRST", 
                    # "NRST", 
                    # "tr_APT1", 
                    # "APT1", 
                    # "tr_APT2", 
                    # "APT2", 
                    
                    "lnPop", 
                    "lnFam", 
                    "lnUR", 
                    "lnLFPR", 
                    "lnMort", 
                    "lnInc_med", 
                    "lnInc_Cwkids",
                    
                    "lnStarts_total", 
                    "lnStarts_single", 
                    "lnStarts_semi", 
                    "lnStarts_row", 
                    
                    "lnCompl_total", 
                    "lnCompl_single", 
                    "lnCompl_semi", 
                    "lnCompl_row"
          ),
          covariate.labels = c("NRST interaction",
                               "ABT1 interaction",
                               "ABT2 interaction",
                               
                               # "NRST regional dummy",
                               # "NRST post-treatment dummy",
                               # "ABT1 regional dummy",
                               # "ABT1 post-treatment dummy",
                               # "ABT2 regional dummy",
                               # "ABT2 post-treatment dummy",
                               
                               "Population",
                               "Number of Families",
                               "Unemployment rate",
                               "Labour force participation rate",
                               "Mortgage rate",
                               "Median income",
                               "Income of couples with kids",
                               
                               "Total construction starts",
                               "\\ \\ \\ \\ \\ Starts on single-detached units",
                               "\\ \\ \\ \\ \\ Starts on semi-detached units",
                               "\\ \\ \\ \\ \\ Starts on row units",
                               "Total construction completions",
                               "\\ \\ \\ \\ \\ Completed single-detached units",
                               "\\ \\ \\ \\ \\ Completed semi-detached units",
                               "\\ \\ \\ \\ \\ Completed row units",
                               escape = FALSE
          ),
          # omit = c("NRST regional dummy", "NRST post-treatment dummy", "ABT1 regional dummy",
          #                      "ABT1 post-treatment dummy", "ABT2 regional dummy",
          #                      "ABT2 post-treatment dummy"),
          notes = c("all variables are log transformations,  ∗ p<0.1; ∗∗ p<0.05; ∗∗∗ p<0.01"),
          notes.append = FALSE,
          column.separate = c(1, 1),
          omit.stat = c("f", "ser","rsq"))
```

_Note_: The table above shows the results of the fixed effects difference-in-differences model. The dependent variable is the logarithmic transformation of the New Housing Price Index and the first column corresponds to the base fixed effects model.


